Smart Drill-Down

### 2015-02-12 TableSummarization/Paper/TableSummarization.tex
length reduction and small changes
changes to related, to intro
small changes
Changes to paper
Changed image font size, and some other changes

\documentclass{vldb}
\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)
\usepackage{enumitem}
\usepackage{times}
\usepackage{subfigure}
\let\proof\relax
\let\endproof\relax
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx,color}
\usepackage{verbatim}
\usepackage{framed}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{framed}
\usepackage[normalem]{ulem}

@@

\newcommand{\agp}[1]{\textcolor{red}{Aditya: #1}}
\newcommand{\mrj}[1]{\textcolor{green}{#1}}
\newcommand{\agpdel}[1]{\textcolor{blue}{\bf ||Del: #1||}}

@@

@@

\begin{abstract}
We present {\em smart drill-down},
an operator for interactively exploring a relational table
to discover and summarize ``interesting'' groups of tuples.
Each group of tuples is described by a {\em rule}.
For instance, the rule $(a, b, \star, 1000)$ tells us that
there are a thousand tuples with value $a$ in the first column and $b$
in the second column (and any value in the third column).
Smart drill-down presents an analyst with a list of rules that
together describe interesting aspects of the table.
The analyst can tailor the definition of interesting,
and can interactively apply smart drill-down on an existing rule to
explore that part of the table.
We demonstrate that the underlying optimization problems 
are {\sc NP-Hard}, and describe an
algorithm for finding the approximately optimal list of rules to display when the user uses a smart drill-down, and a dynamic sampling scheme for efficiently interacting with large tables. Finally, we
perform experiments on real datasets to demonstrate the usefulness of smart drill-down and study the performance of our algorithms.
\end{abstract}

@@

{\small
\bibliographystyle{abbrv}
\bibliography{TableSummarization}  
}

>>>>

\documentclass{sig-alternate}
\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)
\usepackage{enumitem}
\usepackage{times}
\usepackage{subfigure}
\let\proof\relax
\let\endproof\relax
\usepackage{amsmath,amssymb,amsthm}
\usepackage{graphicx,color}
\usepackage{verbatim}
\usepackage{framed}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{framed}
\usepackage[normalem]{ulem}

\usepackage[font={small,it}]{caption}

@@

\newcommand{\agp}[1]{\textcolor{green}{Aditya: #1}}
\newcommand{\mrj}[1]{\textcolor{red}{#1}}
\newcommand{\mrjdel}[1]{\textcolor{red}{\sout{#1}}}

@@

\newenvironment{denselist}{
    \begin{list}{\small{$\bullet$}}%
    {\setlength{\itemsep}{0ex} \setlength{\topsep}{0ex}
    \setlength{\parsep}{0pt} \setlength{\itemindent}{0pt}
    \setlength{\leftmargin}{1.5em}
    \setlength{\partopsep}{0pt}}}%
    {\end{list}}

@@

\begin{abstract}
We present {\em smart drill-down},
an operator for interactively exploring a relational table
to discover and summarize ``interesting'' groups of tuples.
Each group of tuples is described by a {\em rule}.
For instance, the rule $(a, b, \star, 1000)$ tells us that
there are a thousand tuples with value $a$ in the first column and $b$
in the second column (and any value in the third column).
Smart drill-down presents an analyst with a list of rules that
together describe interesting aspects of the table.
The analyst can tailor the definition of interesting,
and can interactively apply smart drill-down on an existing rule to
explore that part of the table.
We demonstrate that the underlying optimization problems 
are {\sc NP-Hard}, and describe an
algorithm for finding the approximately optimal list of rules to display when the user uses a smart drill-down, and a dynamic sampling scheme for efficiently interacting with large tables. Finally, we
perform experiments on real datasets on our experimental prototype to demonstrate the usefulness of smart drill-down and study the performance of our algorithms.
\end{abstract}

@@

\balance
{\small
\bibliographystyle{abbrv}
\bibliography{TableSummarization}  
}

### 2015-02-12 TableSummarization/Paper/conc.tex
Changes to paper
Changed image font size, and some other changes

Our experimental results show that smart drill down
is fast enough to be interactive under various
realistic scenarios. We also showed that the accuracy is high
when sampling is used, and when the maximum weight ($m_w$)
approximation is used.

>>>>

Our experimental results on our experimental prototype show that smart drill down
is fast enough to be interactive under various
realistic scenarios. We also showed that the accuracy is high
when sampling is used, and when the maximum weight ($m_w$)
approximation is used. Moreover, we have a tunable parameter $minSS$ that the user can tweak to tradeoff performance of smart drill down for the accuracy of the rules.

### 2015-02-12 TableSummarization/Paper/exp.tex
Changed image font size, and some other changes

@@

\subsection{Qualitative Study}
We first perform a qualitative study of smart drill down. We observe the effects of various user interface operations on the Marketing Dataset (the results are similar on the Census dataset), and then try out a few different weight functions to study their effects.
\subsubsection{User interface testing}
We now present the rule-based summaries displayed as a result of a few different user actions.

@@

Now suppose the user decides to further explore the table, by looking at education related information of females in the dataset. Say the user clicks on the $\star$ in the `Education' column of the second rule. This opens up Figure~\ref{fig:uiexamplestar} that shows the number of females with different levels of education, for the $4$ most frequent levels of education among females.

Instead of expanding the `Education' column, if the user had simply expanded the third rule, it would have displayed Figure~\ref{fig:uiexamplerule}.

@@

>>>>

\begin{figure}
\vspace{-5pt}
\centering
\includegraphics[width=90mm]{graphs/screenshots6col/age_drilldown.jpg}
\caption{A regular drill down on Age\label{fig:drilldownexample}}
\end{figure}

@@

\subsection{Qualitative Study}
We first perform a qualitative study of smart drill down. We observe the effects of various user interface operations on the Marketing Dataset (the results are similar on the Census dataset), and then try out different weight functions to study their effects.
\subsubsection{User interface testing}
We now present the rule-based summaries displayed as a result of a few different user actions.

@@

Now suppose the user decides to further explore the table, by looking at education related information of females in the dataset. Say the user clicks on the $\star$ in the `Education' column of the second rule. This opens up Figure~\ref{fig:uiexamplestar} that shows the number of females with different levels of education, for the $4$ most frequent levels of education among females. Instead of expanding the `Education' column, if the user had simply expanded the third rule, it would have displayed Figure~\ref{fig:uiexamplerule}.

@@

A regular drill down can be thought of as a special case of smart drill-down with the right weighting function and number of rules. We use this to perform a drill down on the `Age' column using our experimental prototype. The result is shown in Figure~\ref{fig:drilldownexample}. We can contrast it with Figure~\ref{fig:uiexample1}; the latter gives information about multiple columns at once and only displays high count values. Regular drill down on the other hand, serves a complementary purpose by focusing on detailed evaluation of a single column.

### 2015-02-12 TableSummarization/Paper/sampling.tex
Changed image font size, and some other changes

\papertext{
BRS makes multiple passes over the table in order to determine the best set of rules to display. This can be really slow when the table is too large to fit in main memory. We can reduce the response time of smart drill down by running BRS on a sample of the table instead, trading off accuracy of our rules for performance. If we had obtained a sample $s$ by selecting each table tuple with probability $p$, and run BRS on $s$, then we multiply the count of each rule found by BRS, by $\frac{1}{p}$ to estimate its count over the full table.

@@

At any point, we have a tree $U$ of rules displayed to the user. Initially, the tree consists of a single node corresponding to the empty rule. When the user drills down on a rule $r$, the sub-rules of $r$ obtained by running BRS are added as children of node $r$. 
Our system maintains multiple samples in memory, with upto one sample per rule in $U$. Specifically, for each rule $r \in U$, we choose an integer $n_r$, and create a sample $s_r$ consisting of $n_r$ uniformly randomly chosen tuples covered by $r$ from the table. Because of the memory constraint, we must have $\sum_{r\in U} n_r \leq M$.

@@

\item \textbf{Create:} If \textbf{Combine} doesn't work either, then the SampleHandler needs to create a new sample $s$ with $f_s = r$ by making a pass through the table.  Since accessing the hard disk and making a pass through the entire table is a bottleneck, it also creates samples for rules other than $r$ and augments existing samples in the same pass. It first uses the algorithm from Section~\ref{sec:sampling_algorithms} to determine how many tuples to sample for each rule, and uses reservoir sampling~\cite{maibdr1983,Vitter:1985:RSR:3147.3165} to create a uniformly random sample of a given size for each rule.
\squishend
}

>>>>

\papertext{
BRS makes multiple passes over the table in order to determine the best set of rules to display. This can be slow when the table is too large to fit in main memory. We can reduce the response time of smart drill down by running BRS on a sample of the table instead, trading off accuracy of our rules for performance. If we had obtained a sample $s$ by selecting each table tuple with probability $p$, and run BRS on $s$, then we multiply the count of each rule found by BRS, by $\frac{1}{p}$ to estimate its count over the full table.

@@

At any point, we have a tree $U$ of rules displayed to the user. Initially, the tree consists of a single node corresponding to the empty rule. When the user drills down on a rule $r$, the sub-rules of $r$ obtained by running BRS are added as children of node $r$. 
Our system maintains multiple samples in memory, with one sample per rule in $U$. Specifically, for each rule $r \in U$, we choose an integer $n_r$, and create a sample $s_r$ consisting of $n_r$ uniformly randomly chosen tuples covered by $r$ from the table. Because of the memory constraint, we must have $\sum_{r\in U} n_r \leq M$.

@@

\item \textbf{Create:} If \textbf{Combine} doesn't work either, then the SampleHandler needs to create a new sample $s$ with $f_s = r$ by making a pass through the table.  Since accessing the hard disk is expensive, it also creates samples for rules other than $r$ and augments existing samples in the same pass. It first deletes all existing samples, then uses the algorithm from Section~\ref{sec:sampling_algorithms} to determine how many tuples to sample for each rule, and uses reservoir sampling~\cite{maibdr1983,Vitter:1985:RSR:3147.3165} to create a uniformly random sample of a given size for each rule.
\squishend
}
